---
title: "Final Project"
author: "Jeremy Sanchez"
date: "7/8/2019"
output: html_document
---
#Redesigning the Penalty Box
- expected goal model
    counterfactual
      regular shot vs penalty ones
    may also take into account passing to another player. maybe a later step.
- pentalty events

STATSBOMB event data, I can see that, of course.
expected goals modeled for all of that data. 
there is no shot taken in penalty events
  1. build our own expected goals model
     2. But they are from different games, which would explain the differing lists.
     So we will separate the data, so you already have a leg up on this.
        grid of min and max expected goals
View(info)  


# 'Evaluating' Passing 
STATSBOMB data. 
  location and who would intended to.
1. could identify who is expected target of pass as project
2. model for pass receiver  
   - negative sums?
   - may use MLSA 2018 data

  -pass completion model

3. Place a value on a pass (expected goals/pass)
take from beginning (e goals), or end (e goals)
STATSBOMB 
  track sequence of passes and say:
    pass 1 to pass 2 (shot within 5 seconds?)
    pass 2 to pass 3 (shot within 5 seconds?)
    pass 3 to pass 4
    pass 4 to pass 5 (no shot)
    
classification or expected goals of shot to take

Previous Literature: Pass Risk-Reward

Use a weighting to help with pass sequence-ing.

## Expected Goals Per Pass
Step 1: Getting Data the way we want it.
```{r}
View(head(EventDF))
View(head(firstMatch, n = 16L))

cbind(firstMatch$id, firstMatch$related_events)

EventDF.2 <- within(EventDF, rm('player.id','position.id','pass.recipient.id','pass.height.id','pass.body_part.id','pass.type.id','pass.outcome.id','ball_receipt.outcome.id','dribble.outcome.id','shot.body_part.id',
                     'shot.type.id','shot.outcome.id','goalkeeper.technique.id','goalkeeper.position.id',
                     'goalkeeper.body_part.id','goalkeeper.outcome.id','goalkeeper.type.id',
                     'interception.outcome.id','foul_committed.card.id','foul_committed.type.id', 
                     'duel.type.id','duel.outcome.id','50_50.outcome.id','substitution.outcome.id',
                     'substitution.replacement.id','bad_behaviour.card.id'))


library(tidyverse)
EventDF.2 %>% group_by(., possession) %>% slice()

firstMatch <- EventDF.2[1:2720,] 
View(head(firstMatch,n = 40L))

#Version 2.
firstMatch %>% filter(type.name == "Pass" | type.name == "Shot") %>% select(possession,type.name, minute,second, duration, possession_team.name, location, pass.end_location,shot.end_location, shot.statsbomb_xg) -> passes

passes %>% group_by(possession) %>% mutate(length = n()) -> passes
View(head(passes, n = 40L))

passes$x_location = 1:978
passes$y_location = 1:978
passes$x_endlocation = 1:978
passes$y_endlocation = 1:978

for(ii in 1:nrow(passes)) {
  passes$x_location[ii] = passes$location[[ii]][1]
  passes$y_location[ii] = passes$location[[ii]][2]
}

passes$x_endlocation = 1:978
passes$y_endlocation = 1:978

for(jj in 1:nrow(passes)) {
  if(!is.null(passes$pass.end_location[[jj]])) {
    passes$x_endlocation[[jj]] = passes$pass.end_location[[jj]][1]
    passes$y_endlocation[[jj]] = passes$pass.end_location[[jj]][2]
  } else {
    passes$x_endlocation[[jj]] = -99
    passes$y_endlocation[[jj]] = -99
  }
}

warnings()

View(head(passes, n = 80L))

passes %>% group_by(., possession) %>% mutate(sequence = rev(seq(1,n())))

passes$shot.statsbomb_xg<- ifelse(is.na(passes$shot.statsbomb_xg), 0, passes$shot.statsbomb_xg)




View(head(passes, n = 80L))
?seq
```
## RESEARCH QUESTIONS:
1. What can we summarize from a sequence of passes?
2. What are we expected goal per pass?
3. 

```{r}

```
    
  

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
